---
title: "Project1"
author: "Sophie Shao, Sophia Yang, Han (Andy) Xu, Ken Bai, Shenyi (Elaine) Ge"
date: "10/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)

#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## Getting Data Ready for Analysis


```{r, cache=TRUE}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into knn has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))
str(telemm)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
```


## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000)
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, -match("yyes",names(tele_norm))]
tele_test <- tele_norm[test_set, -match("yyes",names(tele_norm))]

#Now the response (aka Labels) - only the yyes column
tele_train_labels <- tele_norm[-test_set, "yyes"]
tele_test_labels <- tele_norm[test_set, "yyes"]
summary(tele_train)
```

## Libraries
```{r}
library(neuralnet)
library(gmodels)
library(caret)
library(class)
threshold <- 0.6
```

## clustering

```{r}

set.seed(123)

tele_norm_cluster <- tele_norm[, -match("yyes",names(tele_norm))]

tele_clusters <- kmeans(tele_norm_cluster, 5)

## Step 4: Evaluating model performance ----
# look at the size of the clusters
tele_clusters$size

# look at the cluster centers
tele_clusters$centers
tele_clusters$cluster

tele_norm_cluster$cluster <- tele_clusters$cluster
tele_norm_cluster$yyes <- tele_norm$yyes

tapply(tele_norm_cluster$yyes, tele_norm_cluster$cluster, mean)
aggregate(data=tele_norm_cluster, yyes~cluster, mean)

#use 4 datasets for 4 clusters, 3 models each dataset

#combined: if 2/3 models say 1, it will be 1


str(tele_norm_cluster$cluster)
#create 4 datasets

cluster_1 <- tele_norm_cluster[tele_norm_cluster$cluster==1,]
cluster_2 <- tele_norm_cluster[tele_norm_cluster$cluster==2,]
cluster_3 <- tele_norm_cluster[tele_norm_cluster$cluster==3,]
cluster_4 <- tele_norm_cluster[tele_norm_cluster$cluster==4,]
cluster_5 <- tele_norm_cluster[tele_norm_cluster$cluster==5,]
```


> Now you are ready to build your ANN model. Feel free to modify the data load, cleaning and preparation code above as per your preference.

### ANN Model
```{r}
teleann_train <- tele_norm[-test_set,]
teleann_test <- tele_norm[test_set,-match("yyes",names(tele_norm))]
tele_train_labels <- tele_norm[-test_set, "yyes"]
tele_test_labels <- tele_norm[test_set, "yyes"]
teleann_model <- neuralnet(formula = yyes ~ ., data = teleann_train)
plot(teleann_model)
```

### Evaluate ANN Model
```{r, cache=TRUE}
teleann_pred <- predict(teleann_model, tele_test)
teleann_pred <- ifelse(teleann_pred < threshold, 0, 1)
CrossTable(x = teleann_test$yyes, y = teleann_pred, prop.chisq=FALSE)
model1results=confusionMatrix(as.factor(teleann_pred), as.factor(teleann_test$yyes), positive = "1")
```

### Improve ANN Model
```{r, cache=TRUE}
teleann_model_improved <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden = c(5,3))

teleann_model_1 <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(2), threshold=0.1)

teleann_model_1a <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(2,2), threshold=0.1, stepmax=10^6)

teleann_model_1b <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(1), threshold=0.1, stepmax=10^6, learningrate=0.01)

teleann_model_1c <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(5), threshold=0.01)

teleann_model_1d <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(5,2), threshold=0.05)

teleann_model_1e <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(1,2), threshold=0.1, stepmax=10^10, learningrate=0.01)


teleann_model_1g <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(10,5), threshold=0.1, stepmax=10^10, learningrate=0.001)

teleann_model_1h <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden=c(5,3), threshold=0.01)
```

### Final ANN Model

```{r, cache=TRUE}
teleann_model <- neuralnet(formula = yyes ~ ., data = tele_ann_train_1, hidden=c(2), threshold=0.01, stepmax=10^10, learningrate=0.001)

```

## KNN Model & Evaluation
```{r, cache=TRUE}
teleknn_pred <- knn(train = tele_train, test = tele_test, cl = tele_train_labels, k = sqrt(nrow(tele_train)))
CrossTable(x = tele_test_labels, y = teleknn_pred, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_pred), as.factor(tele_test_labels), positive = "1")
```

## Improve KNN Model
```{r}
#We want to lower the k value because the data is skewed, and we ended up with k = 70 since it yields the best performing model
teleknn_pred1 <- knn(train = tele_train, test = tele_test, cl = tele_train_labels, k = 70)
CrossTable(x = tele_test_labels, y = teleknn_pred1, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_pred1), as.factor(tele_test_labels), positive = "1")
## Logistic Regression
```{r}
str(tele)
summary(tele)
```

## Getting Train and Test Samples for logistic regression
```{r}
#tele_log_model <- glm(y~ age +job + education, data=tele_train_log, family="binomial")
tele_train$y <- tele_train_labels
tele_test$y <- tele_test_labels
tele_log_model <- glm(y~., data = tele_train, family = "binomial")
#summary(tele_log_model)
predict_values <- predict(tele_log_model, newdata=tele_test, type="response")
modpred <- as.factor(ifelse(predict_values <= threshold, 0, 1))
CrossTable(x = tele_test_labels, y = modpred, prop.chisq=FALSE)
confusionMatrix(modpred, as.factor(tele_test_labels), positive = "1")
```



### Cluster 1

```{r}

#ANN model

test_set1 <- sample(1:nrow(cluster_1), 1000) 
tele_train_labels1 <- cluster_1[-test_set1, "yyes"]
tele_test_labels1 <- cluster_1[test_set1, "yyes"] #KNN needs outcome in both
tele_ann_train_1 <- cluster_1[-test_set1, ]
tele_ann_train_1$yyes <- ifelse(tele_ann_train_1$yyes > 0, .9, .1) #only for ANN & logistic
tele_test_1 <- cluster_1[test_set1,-match("yyes",names(cluster_1))]

plot(teleann_model_1)
model_results <- compute(teleann_model_1, teleann_test_1)
# obtain predicted strength values
predicted_strength <- model_results$net.result
model_results <- ifelse(predicted_strength>threshold, 1,0) #convert thresholds
# examine the correlation between predicted and actual values
cor(predicted_strength, tele_test_labels1)
CrossTable(x = tele_test_labels1, y = model_results, prop.chisq = FALSE)
confusionMatrix(as.factor(model_results), as.factor(tele_test_labels1), positive = "1")

#KNN labels should be separated

model_results <- compute(teleann_model_1h, teleann_test_1)
# obtain predicted strength values
predicted_strength <- model_results$net.result
model_results <- ifelse(predicted_strength>threshold, 1,0) #convert thresholds
# examine the correlation between predicted and actual values
cor(model_results, tele_test_labels1)
CrossTable(x = tele_test_labels1, y = model_results, prop.chisq = FALSE)
confusionMatrix(as.factor(model_results), as.factor(tele_test_labels1), positive = "1")

```

### Cluster 2

```{r, cache=TRUE}
set.seed(12345)
test_set2 <- sample(1:nrow(cluster_2), 2500)
tele_train_labels2 <- cluster_2[-test_set2, "yyes"]
tele_test_labels2 <- cluster_2[test_set2, "yyes"]
teleknn_train_2 <- cluster_2[-test_set2,]
teleknn_test_2 <- cluster_2[test_set2,]
#teleknn_model2 <- knn(train = teleknn_train_2, test = teleknn_test_2, cl = tele_train_labels2, k = sqrt(nrow(teleknn_train_2)))
teleknn_model2_improved <- knn(train = teleknn_train_2, test = teleknn_test_2, cl = tele_train_labels2, k = 5)
CrossTable(x = tele_test_labels2, y = teleknn_model2_improved, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_model2_improved), as.factor(tele_test_labels2), positive = "1")

#ANN Model
tele_ann_train_2 <- cluster_2[-test_set2, ]
tele_test_2 <- cluster_2[test_set2,-match("yyes",names(cluster_2))]
tele_ann_train_2$yyes <- ifelse(tele_ann_train_2$yyes > 0, .9, .1) #only for ANN
teleann_model2 <- neuralnet(formula = yyes ~ ., data = tele_train_2, hidden=c(5,3))
plot(teleann_model_2)

model_results <- compute(teleann_model_2, tele_test_2)
# obtain predicted strength values
predicted_strength <- model_results$net.result
# examine the correlation between predicted and actual values
cor(predicted_strength, tele_test_labels2)
CrossTable(x = tele_test_labels2, y = teleann_model2, prop.chisq = FALSE)
confusionMatrix(as.factor(teleann_model2), as.factor(tele_test_labels2), positive = "1")

```

### Cluster 3
```{r, cache=TRUE}
set.seed(12345)
test_set3 <- sample(1:nrow(cluster_3), 2500)
tele_train_labels3 <- cluster_3[-test_set3, "yyes"]
tele_test_labels3 <- cluster_3[test_set3, "yyes"]
tele_train_3 <- cluster_3[-test_set3,]
tele_test_3 <- cluster_3[test_set3,]
#teleknn_model3 <- knn(train = teleknn_train_3, test = teleknn_test_3, cl = tele_train_labels3, k = sqrt(nrow(teleknn_train_3)))
teleknn_model3_improved <- knn(train = tele_train_3, test = tele_test_3, cl = tele_train_labels3, k = 5)
CrossTable(x = tele_test_labels3, y = teleknn_model3_improved, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_model3_improved), as.factor(tele_test_labels3), positive = "1")

#ANN Model

tele_ann_train_3 <- cluster_3[-test_set3, ]
tele_test_3 <- cluster_3[test_set3,-match("yyes",names(cluster_3))]
tele_ann_train_3$yyes <- ifelse(tele_ann_train_3$yyes > 0, .9, .1) #only for ANN
teleann_model3 <- neuralnet(formula = yyes ~ ., data = tele_train_3, hidden=c(5,3))
plot(teleann_model_3)

model_results <- compute(teleann_model3, tele_test_3)
# obtain predicted strength values
predicted_strength <- model_results$net.result
# examine the correlation between predicted and actual values
cor(predicted_strength, tele_test_labels3)
CrossTable(x = tele_test_labels3, y = teleann_model3, prop.chisq = FALSE)
confusionMatrix(as.factor(teleann_model3), as.factor(tele_test_labels3), positive = "1")
```

### Cluster 4

```{r}
set.seed(12345)
test_set4 <- sample(1:nrow(cluster_4), 1500)
tele_train_labels4 <- cluster_4[-test_set4, "yyes"]
tele_test_labels4 <- cluster_4[test_set4, "yyes"]
teleknn_train_4 <- cluster_4[-test_set4,]
teleknn_test_4 <- cluster_4[test_set4,]
#teleknn_model4 <- knn(train = teleknn_train_4, test = teleknn_test_4, cl = tele_train_labels4, k = sqrt(nrow(teleknn_train_4)))
teleknn_model4_improved <- knn(train = teleknn_train_4, test = teleknn_test_4, cl = tele_train_labels4, k = 1)
CrossTable(x = tele_test_labels4, y = tele_model4_improved, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_model4_improved), as.factor(tele_test_labels4), positive = "1")


#ANN Model
tele_ann_train_4 <- cluster_4[-test_set4, ]
tele_test_4 <- cluster_4[test_set4,-match("yyes",names(cluster_4))]
tele_ann_train_4$yyes <- ifelse(tele_ann_train_4$yyes > 0, .9, .1) #only for ANN

teleann_model4 <- neuralnet(formula = yyes ~ ., data = tele_train_4, hidden=c(5,3))
plot(teleann_model_4)

model_results <- compute(teleann_model4, tele_test_4)
# obtain predicted strength values
predicted_strength <- model_results$net.result
# examine the correlation between predicted and actual values
cor(predicted_strength, tele_test_labels4)
CrossTable(x = tele_test_labels4, y = teleann_model4, prop.chisq = FALSE)
confusionMatrix(as.factor(teleann_model4), as.factor(tele_test_labels4), positive = "1")
```

### Cluster 5

```{r}
set.seed(12345)
test_set5 <- sample(1:nrow(cluster_5), 2500)
tele_train_labels5 <- cluster_5[-test_set5, "yyes"]
tele_test_labels5 <- cluster_5[test_set5, "yyes"]
teleknn_train_5 <- cluster_5[-test_set5,]
teleknn_test_5 <- cluster_5[test_set5,]
#teleknn_model5 <- knn(train = teleknn_train_5, test = teleknn_test_5, cl = tele_train_labels5, k = sqrt(nrow(teleknn_train_5)))
teleknn_model5_improved <- knn(train = teleknn_train_5, test = teleknn_test_5, cl = tele_train_labels5, k = 1)
CrossTable(x = tele_test_labels5, y = tele_model5_improved, prop.chisq = FALSE)
confusionMatrix(as.factor(tele_model5_improved), as.factor(tele_test_labels5), positive = "1")

#ANN Model

tele_ann_train_5 <- cluster_5[-test_set5, ]
tele_test_5 <- cluster_5[test_set5,-match("yyes",names(cluster_5))]
tele_ann_train_5$yyes <- ifelse(tele_ann_train_5$yyes > 0, .9, .1) #only for ANN
teleann_model5 <- neuralnet(formula = yyes ~ ., data = tele_train_5, hidden=c(5,3))
plot(teleann_model_5)

model_results <- compute(teleann_model5, tele_test_5)
# obtain predicted strength values
predicted_strength <- model_results$net.result
# examine the correlation between predicted and actual values
cor(predicted_strength, tele_test_labels5)
CrossTable(x = tele_test_labels5, y = teleann_model5, prop.chisq = FALSE)
confusionMatrix(as.factor(teleann_model5), as.factor(tele_test_labels5), positive = "1")
```


