---
title: "Project1"
author: "Sophie Shao, Sophia Yang, Han (Andy) Xu, Ken Bai"
date: "10/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Downloading and Prepping the Data

```{r}
#Downloading and Prepping the Data
tele <- read.csv("tele.csv", stringsAsFactors = TRUE)
summary(tele)

#We are deleting the "duration" variable because it is an after the fact measurement. We only should be using variables that we know before the call
tele$duration <- NULL

# Deleting the column X
tele$X <- NULL

# Changing pdays to a dummy and deleting pdays
tele$pdaysdummy <- ifelse(tele$pdays == 999, 0, 1)
tele$pdays <- NULL

str(tele)
```

## Getting Data Ready for Analysis

```{r, cache=TRUE}
# Using model.matrix to convert all the factors to dummy variables
# We are converting all of the factors into dummy variables as the input into knn has to be numeric

telemm <- as.data.frame(model.matrix(~.-1,tele))
str(telemm)

# Randomize the rows in the data (shuffling the rows)
set.seed(12345)
tele_random <- telemm[sample(nrow(telemm)),]

#Normalize the data
normalize <- function(x) {
  return ((x - min(x)) / (max(x) - min(x)))
}

# we are going to normalize everything 
tele_norm <- as.data.frame(lapply(tele_random, normalize))
```


## Getting Train and Test Samples

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set <- sample(1:nrow(tele_norm), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train <- tele_norm[-test_set, -match("yyes",names(tele_norm))]
tele_test <- tele_norm[test_set, -match("yyes",names(tele_norm))]

#Now the response (aka Labels) - only the yyes column
tele_train_labels <- tele_norm[-test_set, "yyes"]
tele_test_labels <- tele_norm[test_set, "yyes"]
summary(tele_train)
```

> Now you are ready to build your ANN model. Feel free to modify the data load, cleaning and preparation code above as per your preference.

## ANN Model
```{r}
teleann_train <- tele_norm[-test_set,]
teleann_test <- tele_norm[test_set,]
library(neuralnet)
teleann_model <- neuralnet(formula = yyes ~ ., data = teleann_train)
plot(teleann_model)
```

## Evaluate ANN Model
```{r, cache=TRUE}
library(gmodels)
library(caret)
library(class)
teleann_pred <- predict(teleann_model, tele_test)
threshold <- 0.6
teleann_pred <- ifelse(teleann_pred < threshold, 0, 1)

CrossTable(x = teleann_test$yyes, y = teleann_pred, prop.chisq=FALSE)
confusionMatrix(as.factor(teleann_pred), as.factor(teleann_test$yyes), positive = "1")
```

## Improve ANN Model
```{r, cache=TRUE}
#teleann_model <- neuralnet(formula = yyes ~ ., data = teleann_train, hidden = 5)
```

## KNN Model & Evaluation
```{r, cache=TRUE}
teleknn_pred <- knn(train = tele_train, test = tele_test, cl = tele_train_labels, k = sqrt(nrow(tele_train)))
CrossTable(x = tele_test_labels, y = teleknn_pred, prop.chisq = FALSE)
confusionMatrix(as.factor(teleknn_pred), as.factor(tele_test_labels), positive = "1")
```

## Improve KNN Model
```{r}
#To be finished..
```

## Logistic Regression
```{r}
str(tele)
summary(tele)

## Getting Train and Test Samples for logistic regression

```{r}
# Selects 10000 random rows for test data
set.seed(12345)
test_set_log <- sample(1:nrow(tele), 10000) 
# Depending on R-version and computer, different rows may be selected. 
# If that happens, results are different. 

# Create a train set and test set
#First the predictors - all columns except the yyes column
tele_train_log <- tele[-test_set_log, ]
tele_test_log <- tele[test_set_log, -match("y",names(tele))]


#Now the response (aka Labels) - only the y column
tele_train_labels_log <- tele[-test_set_log, "y"]
tele_test_labels_log <- tele[test_set_log, "y"]
summary(tele_train_log)
str(tele_train_log)

tele_log_model <- glm(y~ ., data=tele_train_log, family="binomial")
summary(tele_log_model)

predict_values <- predict(tele_log_model, newdata=tele_test_log, type="response")
```
